Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2023-01-11 edubots_surveys.Rnw
Update edubots_surveys.Rnw
Co-authored-by: Francisco Barranco <fbarranco@ugr.es>

Our initial intention in the design of these surveys was to probe the opinions
of tertiary education teachers in the introduction of chatbot technologies in
class. We wanted to find the answer to four research questions, of which the
first was to check whether teachers already used some kind of messaging
application, and the one they preferred. The availability of certain
technologies for implementing chatbots may vary based on the outcome. In this
sense, the design of the survey introduced some ambiguity on what we really
consider ``messaging technology'', that was any way validated in the piloting
phase of the survey, and eventually resolved by the answers.  Apparently,
anything that sends messages (even if they are not instant messages or have no
dedicated application) was the concept in the minds of the surveyed. In this
case, we would like to add a clarification. While we had in mind, as indicated
by the possible answers, instant messaging applications when we elaborated this
question, we included these institution-provided applications mainly for
completion. But it should be noted that, in most cases, they are not {\em
  instant} messaging apps in the way Telegram or Facebook Messenger are; they
are messaging facilities provided by learning management systems such as Moodle
or Blackboard. So the answer to this question must be understood in two
different ways: their preference for the {\em provider} of the technology (the
university itself, any company) as well as the {\em type} of technology
(instant, app-based messaging systems vs. web- or email-based messaging systems
integrated in another learning management system).

>>>>

Our initial intention in the design of these surveys was to probe the opinions
of tertiary education teachers in the introduction of chatbot technologies in
class. We wanted to find the answer to four research questions, of which the
first was to check whether teachers already used some kind of messaging
application, and the one they preferred. The availability of certain
technologies for implementing chatbots may vary based on the outcome. In this
sense, the design of the survey introduced some ambiguity on what we really
consider ``messaging technology'', that was anyway validated in the piloting
phase of the survey, and eventually resolved by the answers.  Apparently,
anything that sends messages (even if they are not instant messages or have no
dedicated application) was the concept in the minds of the surveyed. In this
case, we would like to add a clarification. While we had in mind, as indicated
by the possible answers, instant messaging applications when we elaborated this
question, we included these institution-provided applications mainly for
completion. But it should be noted that, in most cases, they are not {\em
  instant} messaging apps in the way Telegram or Facebook Messenger are; they
are messaging facilities provided by learning management systems such as Moodle
or Blackboard. So the answer to this question must be understood in two
different ways: their preference for the {\em provider} of the technology (the
university itself, any company) as well as the {\em type} of technology
(instant, app-based messaging systems vs. web- or email-based messaging systems
integrated in another learning management system).
